---
title: "final_project"
author: "Xintong Liu"
date: "2022-11-17"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Preprocessing
```{r}
# Tiffany's code

# # load in dataset
# adult <- read.csv("adult.csv")
# 
# # revert to factor
# adult$workclass <- as.factor(adult$workclass)
# adult$education <- as.factor(adult$education)
# adult$marital.status <- as.factor(adult$marital.status)
# adult$occupation <- as.factor(adult$occupation)
# adult$relationship <- as.factor(adult$relationship)
# adult$race <- as.factor(adult$race)
# adult$sex <- as.factor(adult$sex)
# adult$native.country <- as.factor(adult$native.country)
# adult$income <- as.factor(adult$income)
# str(adult)
# 
# # replace ? by NA
# for(i in 1:length(adult)) {
#   matches <- grepl("\\?", adult[ ,i])
#   for(j in 1:length(matches)) {
#     ifelse(matches[j] == TRUE, adult[j,i] <- "NA", matches[j])
#   }
# }
# # adult$workclass <- gsub("?",NA,adult$workclass, fixed = TRUE)
# 
# # delete NA
# adult <- na.omit(adult) 
# #table(adult$workclass)
```

```{r}
adult <- read.csv("adult2.csv")
head(adult)
```
-- Work Class Combining

```{r}
table(adult$workclass)
```
```{r}
adult$workclass <- as.character(adult$workclass)

adult$workclass[adult$workclass == "Without-pay" | 
                  adult$workclass == "Never-worked"] <- "Unemployed"

adult$workclass[adult$workclass == "State-gov" |
                  adult$workclass == "Local-gov"] <- "SL-gov"

adult$workclass[adult$workclass == "Self-emp-inc" |
                  adult$workclass == "Self-emp-not-inc"] <- "Self-employed"

table(adult$workclass)
```

-- Marital Status Combining

```{r}
table(adult$marital.status)
```
```{r}
adult$marital.status <- as.character(adult$marital.status)

adult$marital.status[adult$marital.status == "Married-AF-spouse" |
                       adult$marital.status == "Married-civ-spouse" |
                       adult$marital.status == "Married-spouse-absent"] <- "Married"

adult$marital.status[adult$marital.status == "Divorced" |
                       adult$marital.status == "Separated" |
                       adult$marital.status == "Widowed"] <- "Not-Married"
table(adult$marital.status)
```

-- Country Combining

```{r}
adult$native.country <- as.character(adult$native.country)

north.america <- c("Canada", "Cuba", "Dominican-Republic", "El-Salvador", "Guatemala",
                   "Haiti", "Honduras", "Jamaica", "Mexico", "Nicaragua",
                   "Outlying-US(Guam-USVI-etc)", "Puerto-Rico", "Trinadad&Tobago",
                   "United-States")
asia <- c("Cambodia", "China", "Hong", "India", "Iran", "Japan", "Laos",
          "Philippines", "Taiwan", "Thailand", "Vietnam")
south.america <- c("Columbia", "Ecuador", "Peru")
europe <- c("England", "France", "Germany", "Greece", "Holand-Netherlands",
            "Hungary", "Ireland", "Italy", "Poland", "Portugal", "Scotland",
            "Yugoslavia")
other <- c("South", "?")

adult$native.country[adult$native.country %in% north.america] <- "North America"
adult$native.country[adult$native.country %in% asia] <- "Asia"
adult$native.country[adult$native.country %in% south.america] <- "South America"
adult$native.country[adult$native.country %in% europe] <- "Europe"
adult$native.country[adult$native.country %in% other] <- "Other"

table(adult$native.country)
```
```{r}
adult$native.country <- as.factor(adult$native.country)
adult$marital.status <- as.factor(adult$marital.status)
adult$workclass <- as.factor(adult$workclass)
head(adult)
```
-- Dealing with Missing Data

```{r}
table(adult$workclass)
```
```{r}
adult[adult == "?"] <- NA
table(adult$workclass)
```
```{r}
# install.packages("Amelia")
library(Amelia)
```

```{r}
colSums(is.na(adult))
```

```{r}
missmap(adult, y.at = 1, y.labels = "", col = c("yellow", "black"), legend = TRUE)
```

```{r}
# method1: drop rows
adult <- na.omit(adult)

# method2: KNN (running time error?)
# as it is observed only the following coloumns have NAs in them, we specifically perform kNN imputation on these 3 variables

# library(VIM)
# adult<-kNN(adult,variable=c("workclass","occupation"),k=sqrt(nrow(adult)))
```

```{r}
colSums(is.na(adult))
```

```{r}
missmap(adult, y.at = 1, y.label = "", legend = , col = c("yellow", "black"))
```

```{r}
head(adult)
```


## Data Analysis
```{r}
# plot a histogram of ages that is colored by income
library(ggplot2)
ggplot(adult, aes(age)) + geom_histogram(aes(fill = income), color = "black", binwidth = 1)
```
From this plot we can see that the percentage of people who make above 50K peaks out at roughly 35% between ages 30 and 50.

```{r}
# plot a histogram of hours worked per week
ggplot(adult, aes(hours.per.week)) + geom_histogram()
```
The highest frequency of hours.per.week occurs at 40.

```{r}
# income class by region
library(data.table)
setnames(adult, "native.country", "region")

# Reorder factor levels by count
region.ordered <- reorder(adult$region, adult$region, length)
region.ordered <- factor(region.ordered, levels = rev(levels(region.ordered)))

ggplot(adult, aes(region.ordered)) + geom_bar(aes(fill = income), color = "black")
```
```{r}
# correlation of each factors
pairs(~age+fnlwgt+educational.num+capital.gain+capital.loss+hours.per.week, adult)
```
```{r}
# revert to factor
adult$workclass <- as.factor(adult$workclass)
adult$education <- as.factor(adult$education)
adult$marital.status <- as.factor(adult$marital.status)
adult$occupation <- as.factor(adult$occupation)
adult$relationship <- as.factor(adult$relationship)
adult$race <- as.factor(adult$race)
adult$gender <- as.factor(adult$gender)
adult$region <- as.factor(adult$region)
adult$income <- as.factor(adult$income)
str(adult)
```

```{r}
# Box plot 1
ggplot(data = adult, aes(x = income, y = hours.per.week, fill = income)) +
        geom_boxplot() +
        theme_bw() +
        labs(x = "Income", y = "Hours per Week", 
             title = "Graph 1: Boxplot for Income & Hours per Week")
```
```{r}
# Box plot 2
ggplot(data = adult, aes(x = income, y = age, fill = income)) +
        geom_boxplot() +
        theme_bw() +
        labs(x = "Income", y = "Age", 
             title = "Graph 2: Boxplot for Income & Age")
```
```{r}
# Box plot 3
ggplot(data = adult, aes(x = income, y = educational.num, fill = income)) +
        geom_boxplot() +
        theme_bw() +
        labs(x = "Income", y = "Educational Num", 
             title = "Graph 3: Boxplot for Income & Educational Num")
```


## Model Training
The purpose of this model is to classify people into two groups, below 50k or above 50k in income. We will build the model using training data, and then predict the salary class using the test group.

### Logistic Regression

```{r}
# build train and test data
library(caTools)
split <- sample.split(adult$income, SplitRatio = 0.7)
train <- subset(adult, split == TRUE)
test <- subset(adult, split == FALSE)

# train the model
log.model <- glm(income ~ ., family = binomial(), train)

# --------------------- Predicting on train data ------------------------------
# prediciton - confusion matrix, accuracy, recall, and precision
prediction <- predict(log.model, train, type = "response")
cm <- table(train$income, prediction >= 0.5)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])

cm
accuracy
recall
precision

# --------------------- Predicting on test data ------------------------------
# prediciton - confusion matrix, accuracy, recall, and precision
prediction <- predict(log.model, test, type = "response")
cm <- table(test$income, prediction >= 0.5)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])

cm
accuracy
recall
precision
```
Logistic Regression - training
accuracy: 0.8491761
recall: 0.8791106
precision: 0.9268615

Logistic Regression - testing
accuracy: 0.8437364
recall: 0.873219
precision: 0.9267071


### Naive Bayes
```{r}
library(naivebayes)
library(dplyr)
library(ggplot2)
library(psych)

# train the model
NB.model <- naive_bayes(income ~ ., data = train, usekernel = T)
plot(NB.model)
```
```{r}
# --------------------- Predicting on train data -----------------------------
prediction <- predict(NB.model, train)
 
# Confusion Matrix of train data
cm <- table(train$income, prediction)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])
cm
accuracy
recall
precision

# --------------------- Predicting on test data ------------------------------
prediction <- predict(NB.model, test)
 
# Confusion Matrix of test data
cm <- table(test$income, prediction)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])
cm
accuracy
recall
precision
```
Naive Bayes - training
accuracy: 0.8088012
recall: 0.7998871
precision: 0.9945105

Naive Bayes - testing
accuracy: 0.807386
recall: 0.7992251
precision: 0.9933545


### C4.5 (decision trees)
```{r}
library(rJava)
library(RWeka)

# train the model
C45.model <- J48(income ~ ., data = train)
#summary(C45.model)
```
```{r}
# --------------------- Predicting on train data -----------------------------
prediction <- predict(C45.model, train)
 
# Confusion Matrix of train data
cm <- table(train$income, prediction)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])
cm
accuracy
recall
precision

# --------------------- Predicting on test data ------------------------------
prediction <- predict(C45.model, test)
 
# Confusion Matrix of test data
cm <- table(test$income, prediction)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])
cm
accuracy
recall
precision
```
C4.5 - training
accuracy: 0.8798995
recall: 0.8895522
precision: 0.9593858

C4.5 - testing
accuracy: 0.8462708
recall: 0.8686184
precision: 0.9373014


### C5.0 (newer decision trees)
```{r}
library(C50)
library(printr)

# train the model
C50.model <- C5.0(income ~ ., data = train)
#summary(C50.model)
```
```{r}
# --------------------- Predicting on train data -----------------------------
prediction <- predict(C50.model, train)
 
# Confusion Matrix of train data
cm <- table(train$income, prediction)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])
cm
accuracy
recall
precision

# --------------------- Predicting on test data ------------------------------
prediction <- predict(C50.model, test)
 
# Confusion Matrix of test data
cm <- table(test$income, prediction)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])
cm
accuracy
recall
precision
```
C5.0 - training
accuracy: 0.8771374
recall: 0.8905545
precision: 0.9538138

C5.0 - testing
accuracy: 0.8609703
recall: 0.8797451
precision: 0.9441395


### NBTree
```{r}
library("rJava")
library("RWekajars")
library("RWeka")
```

```{r}
WPM("refresh-cache")
WPM("package-info", "repository", "naiveBayesTree")
WPM("install-package", "naiveBayesTree")
```
```{r}
WOW("weka/classifiers/trees/NBTree")
```
```{r}
NBTree <- make_Weka_classifier("weka/classifiers/trees/NBTree")
```

```{r}
# train the model
NBTree.model <- NBTree(income ~ ., data = train)
#print(NBTree.model)
```

```{r}
# --------------------- Predicting on train data -----------------------------
prediction <- predict(NBTree.model, train)
 
# Confusion Matrix of train data
cm <- table(train$income, prediction)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])
cm
accuracy
recall
precision

# --------------------- Predicting on test data ------------------------------
prediction <- predict(NBTree.model, test)
 
# Confusion Matrix of test data
cm <- table(test$income, prediction)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])
cm
accuracy
recall
precision
```
NBTree - training
accuracy: 0.8403004
recall: 0.9235174
precision: 0.8587172

NBTree - testing
accuracy: 0.8338161
recall: 0.9200249
precision: 0.8531253


### Bootstrapped Aggregation (Bagging)
```{r}
library(ipred)
```

```{r}
# train the model
bagging.model <- bagging(income ~ ., data = train)

# --------------------- Predicting on train data -----------------------------
prediction <- predict(bagging.model, train)
 
# Confusion Matrix of train data
cm <- table(train$income, prediction)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])
cm
accuracy
recall
precision

# --------------------- Predicting on test data ------------------------------
prediction <- predict(bagging.model, test)
 
# Confusion Matrix of test data
cm <- table(test$income, prediction)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])
cm
accuracy
recall
precision
```
Bagging - training
accuracy: 0.996338
recall: 0.9960905
precision: 0.9990507

Bagging - testing
accuracy: 0.8470673
recall: 0.8813278
precision: 0.9205432


### Random Forest
```{r}
library(randomForest)
```

```{r}
# train the model
randomForest.model <- randomForest(income ~ ., data = train)

# --------------------- Predicting on train data -----------------------------
prediction <- predict(randomForest.model, train)
 
# Confusion Matrix of train data
cm <- table(train$income, prediction)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])
cm
accuracy
recall
precision

# --------------------- Predicting on test data ------------------------------
prediction <- predict(randomForest.model, test)
 
# Confusion Matrix of test data
cm <- table(test$income, prediction)
accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
recall <- cm[1] / sum(cm[1], cm[2])
precision <- cm[1] / sum(cm[1], cm[3])
cm
accuracy
recall
precision
```
Random Forest - training
accuracy: 0.9478944
recall: 0.9514314
precision: 0.9807661

Random Forest - testing
accuracy: 0.8565532
recall: 0.8801122
precision: 0.9368198

## Plot of Instances vs Acc
```{r}
# library("dplyr")
# library(caTools)
# library(naivebayes)
# library(dplyr)
# library(ggplot2)
# library(psych)
# library(rJava)
# library(RWeka)
# library(C50)
# library(printr)

NB.acc = c()
C45.acc = c()
C50.acc = c()
NBTree.acc = c()
bagging.acc = c()
randomForest.acc = c()

for (i in seq(2500, 45000, 2500)) {
  adult_temp <- sample_n(adult, i)  
  
  split <- sample.split(adult_temp$income, SplitRatio = 0.7)
  train_temp <- subset(adult_temp, split == TRUE)
  test_temp <- subset(adult_temp, split == FALSE)
  
  # Native Bayes
  NB.model.temp <- naive_bayes(income ~ ., data = train_temp, usekernel = T)
  prediction <- predict(NB.model.temp, test_temp)
  cm <- table(test_temp$income, prediction)
  accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
  NB.acc <- c(NB.acc, accuracy*100)
  
  # C4.5
  C45.model.temp <- J48(income ~ ., data = train_temp)
  prediction <- predict(C45.model.temp, test_temp)
  cm <- table(test_temp$income, prediction)
  accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
  C45.acc <- c(C45.acc, accuracy*100)

  # C5.0
  C50.model.temp <- C5.0(income ~ ., data = train_temp)
  prediction <- predict(C50.model.temp, test_temp)
  cm <- table(test_temp$income, prediction)
  accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
  C50.acc <- c(C50.acc, accuracy*100)
 
  # NBTree 
  NBTree.model.temp <- NBTree(income ~ ., data = train_temp)
  prediction <- predict(NBTree.model.temp, test_temp)
  cm <- table(test_temp$income, prediction)
  accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
  NBTree.acc <- c(NBTree.acc, accuracy*100)
  
  # Bagging
  bagging.model.temp.temp <- bagging(income ~ ., data = train_temp)
  prediction <- predict(bagging.model.temp, test_temp)
  cm <- table(test_temp$income, prediction)
  accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
  bagging.acc <- c(bagging.acc, accuracy*100)
  
  # Random Forest
  randomForest.model.temp <- randomForest(income ~ ., data = train_temp)
  prediction <- predict(randomForest.model.temp, test_temp)
  cm <- table(test_temp$income, prediction)
  accuracy <- sum(cm[1], cm[4]) / sum(cm[1:4])
  randomForest.acc <- c(randomForest.acc, accuracy*100)
}

allmodel.acc <- list(NB.acc, C45.acc, C50.acc, NBTree.acc, bagging.acc, randomForest.acc)

par(mfrow = c(1, 1))
plot(NA, ylim = c(79, 87), xlim = c(2500, 45000), xlab="Instances", ylab="Accuracy")

mypal <- colorRampPalette( c( "red", "blue", "green", "gold", "darkgreen", "lightskyblue"))(6)

for(i in 1:6){
  lines(seq(2500, 45000, 2500), allmodel.acc[[i]], type = "l", col = mypal[i], lwd=1.5)
}
legend(x = "topleft", lty = c(4,6), cex = 0.5, legend=c("Naive Bayes", "C4.5", "C5.0", "NBTree", "Bagging", "Random Forest"), col = c("red", "blue", "green", "gold", "darkgreen", "lightskyblue"))
grid(nx = NULL, ny = NULL,
     lty = 3,      # Grid line type
     col = "gray", # Grid line color
     lwd = 1)
```
```{r}
# plot with only Naice-Bayes & C4.5
twomodel.acc <- list(NB.acc, C45.acc)

par(mfrow = c(1, 1))
plot(NA, ylim = c(79.5, 87), xlim = c(2500, 45000), xlab="Instances", ylab="Accuracy")

mypal <- colorRampPalette( c( "red", "blue") )(2)

for(i in 1:2){
  lines(seq(2500, 45000, 2500), twomodel.acc[[i]], type = "l", col = mypal[i], lwd=1.5)
}
legend(x = "right", lty = c(4,6), cex = 1, legend=c("Naive Bayes", "C4.5"), col = c("red", "blue"))
grid(nx = NULL, ny = NULL,
     lty = 3,      # Grid line type
     col = "gray", # Grid line color
     lwd = 1)
```

```{r}
# plot with Naice-Bayes, C4.5, NBTree
threemodel.acc <- list(NB.acc, C45.acc, NBTree.acc)

par(mfrow = c(1, 1))
plot(NA, ylim = c(79, 87), xlim = c(2500, 45000), xlab="Instances", ylab="Accuracy")

mypal <- colorRampPalette( c( "red", "blue", "gold") )(3)

for(i in 1:3){
  lines(seq(2500, 45000, 2500), threemodel.acc[[i]], type = "l", col = mypal[i], lwd=1.5)
}
legend(x = "right", lty = c(4,6), cex = 1, legend=c("Naive Bayes", "C4.5", "NBTree"), col = c("red", "blue", "gold"))
grid(nx = NULL, ny = NULL,
     lty = 3,      # Grid line type
     col = "gray", # Grid line color
     lwd = 1)
```

References:
Adult Datasets: https://archive.ics.uci.edu/ml/datasets/Adult
Kaggle: https://www.kaggle.com/code/kazimanil/adult-census-income-classification
Kaggle (Data Processing + logistic Regression): https://www.kaggle.com/code/flyingwombat/logistic-regression-with-uci-adult-income
Paper: https://www.aaai.org/Papers/KDD/1996/KDD96-033.pdf
Naïve Bayes: https://www.r-bloggers.com/2021/04/naive-bayes-classification-in-r/
C4.5 & C5.0: https://rpubs.com/kjmazidi/195428
NBTree: https://www.harbu.org/posts/2014-11-26-nbtree-in-R.html
More Models: https://machinelearningmastery.com/non-linear-classification-in-r-with-decision-trees/




```{r}
# vector = c()
# values = c(1.12157347682574, 1.33192942183165, 2.08170603538164, 
# 3.21936891077735, 3.87674160966784, 4.01222877372179, 3.97721253044977, 
# 3.92748085243377, 3.89422132704385, 3.87554992373411, 3.86571722337484, 
# 3.86066855038186, 3.85810016465002, 3.85679624059312, 3.85613341785451, 
# 3.85579555076542, 3.85562274484616, 3.85553404933868, 3.85548836742791, 
# 3.85546476209749, 3.85545252710548)
# # for (i in 1:length(values))
# #   vector[i] <- values[i]
# for (i in 1:length(values))
#   vector <- c(vector, values[i])
# 
# vector2 = c()
# values2 = c(1.10529328957704, 1.31478057418982, 
# 2.05843350413484, 3.21445290319435, 3.93127780496161, 4.10019570732597, 
# 4.0548974496435, 3.97577600575589, 3.91388817353566, 3.87397233241435, 
# 3.85011420707963, 3.83631205949334, 3.82843188274012, 3.82395020512325, 
# 3.82139984806649, 3.81994467228049, 3.81911146133043, 3.81863258400429, 
# 3.81835633714707, 3.81819642258335, 3.81810355018493)
# # for (i in 1:length(values2))
# #   vector2[i] <- values2[i]
# for (i in 1:length(values2))
#   vector2 <- c(vector2, values2[i])
# 
# test <- list(vector, vector2)
# 
# par(mfrow = c(1, 1))
# plot(NA, ylim = c(1, 4), xlim = c(0, 10), xlab="Instances", ylab="Accuracy")
# 
# mypal <- colorRampPalette( c( "red", "blue" ) )( 2 )
# 
# for(i in 1:2){
#   lines(test[[i]], type = "l", col = mypal[i], , lwd=1.5)
#   }
```

```{r}
# dat <- list(c(1.12157347682574, 1.33192942183165, 2.08170603538164, 
# 3.21936891077735, 3.87674160966784, 4.01222877372179, 3.97721253044977, 
# 3.92748085243377, 3.89422132704385, 3.87554992373411, 3.86571722337484, 
# 3.86066855038186, 3.85810016465002, 3.85679624059312, 3.85613341785451, 
# 3.85579555076542, 3.85562274484616, 3.85553404933868, 3.85548836742791, 
# 3.85546476209749, 3.85545252710548), c(1.10529328957704, 1.31478057418982, 
# 2.05843350413484, 3.21445290319435, 3.93127780496161, 4.10019570732597, 
# 4.0548974496435, 3.97577600575589, 3.91388817353566, 3.87397233241435, 
# 3.85011420707963, 3.83631205949334, 3.82843188274012, 3.82395020512325, 
# 3.82139984806649, 3.81994467228049, 3.81911146133043, 3.81863258400429, 
# 3.81835633714707, 3.81819642258335, 3.81810355018493), c(1.08732237015566, 
# 1.29744314553374, 2.03681100176799, 3.18820303674863, 3.90649946705568, 
# 4.08059333708303, 4.04639279053423, 3.98156199908701, 3.93264549967637, 
# 3.90244185986869, 3.88514800191734, 3.87554934102343, 3.87028551934942, 
# 3.86740818622607, 3.86583394198314, 3.86497024645408, 3.86449471113229, 
# 3.86423191258367, 3.86408614948732, 3.86400502180298, 3.86395972379237
# ))
# par(mfrow = c(1, 1))
# plot(NA, ylim = c(1, 4), xlim = c(0, 10)) #better view over the lines
# 
# mypal <- colorRampPalette( c( "red", "green", "blue" ) )( 3 )
# 
# for(i in 1:3){
#   lines(dat[[i]], type = "l", col = mypal[i], , lwd=1.5)
#   }
```




